---
title: "Package description"
author: "vkhan"
date: "2024-04-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

# Description of the package

This package contains three functions that can be helpful in calculating different distances for machine learning tasks. These functions are:

* create_distribution
+ calculate_fid
- cossim

In addition, there are two example datasets of distributions.
This is a link to [project repository](https://github.com/valeriya-khan/r_assignment2)

## Create distribution
The first function takes the distribution as an input and returns object of class distribution. The example usage can be seen below:

```{r create_distribution}
library(vkhanassignment2)
wine <- read.table("http://archive.ics.uci.edu/ml/machine-learning-databases/wine/wine.data",
                   sep=",")
wine_distribution1 <- create_distribution(wine[1:6])
wine_distribution1
```

## Calculate fid

The second provided function allows to calculate Frechet Inception distance between two distributions. The usage is as following:

```{r calculate_fid}
library(expm)
library(psych)
wine <- read.table("http://archive.ics.uci.edu/ml/machine-learning-databases/wine/wine.data",
                   sep=",")
wine_distribution1 <- create_distribution(wine[1:6])
wine_distribution2 <- create_distribution(wine[7:12])
calculate_fid(wine_distribution1, wine_distribution2)
plot(wine_distribution1$V1, wine_distribution2$V9)
```

## Calculate cossim
Last function calculates cosine similarity of two given vectors. Example of usage:
```{r cossim}
cossim(c(1,2,3), c(4,5,6))
```

## Datasets
Mean values of each of the dataset columns are as follows:

| Name | Col1 | Col2 | Col3 | Col4 | Col5 | Col6 |
|:-:|:-:|:-:|:-:|:-:|:-:|:-:|
| wine_distribution1 | 1.938202  | 13.000618   | 2.336348   | 2.366517 | 19.494944  | 99.741573  |
| wine_distribution2 | 2.2951124  | 2.0292697  | 0.3618539 | 1.5908989  | 5.0580899  | 0.9574494  |
